Mortar-based entropy stable discontinuous Galerkin methods on non-conforming quadrilateral and hexahedral meshes

### 2020-04-03 docs/ESDG_mortar/main.tex
updating docs

\begin{figure}
\centering
%\subfloat[Coarse $N=3$ non-conforming affine mesh]{\raisebox{2.6em}{\includegraphics[width=.475\textwidth]{figs/mesh_affine.png}}}
\subfloat[$L^2$ errors]{
\begin{tikzpicture}
\begin{loglogaxis}[
    width=.49\textwidth,
    xlabel={Mesh size $h$},
    ylabel={Error}, 
    xmax=1.5,
    ymin=5e-6, ymax=.1,
    legend pos=south east, legend cell align=left, legend style={font=\tiny},	
    xmajorgrids=true, ymajorgrids=true, grid style=dashed,
    legend entries={Lobatto, Gauss}%, Lobatto-Gauss}    
]
\pgfplotsset{
cycle list={{blue, mark=*}, {red, dashed ,mark=square*}}%,{black, dashdotted ,mark=triangle*}}
}
% N = 1
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0302287)(0.5,0.0204278)(0.25,0.00988213)(0.125,0.00383616)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0312387)(0.5,0.020413)(0.25,0.00690005)(0.125,0.0017994)};

% N = 2
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.025246)(0.5,0.00858607)(0.25,0.00156388)(0.125,0.000334682)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0236979)(0.5,0.00616892)(0.25,0.000963938)(0.125,0.000249721)};

@@

\node at (axis cs:2.4,2.8) {$N = 1$};
\node at (axis cs:2.4,1.3) {$N = 2$};
\node at (axis cs:2.4,.6) {$N = 3$};
\end{loglogaxis}
\end{tikzpicture}
}
\hspace{.1em}
\subfloat[$L^{\infty}$ errors]{
\begin{tikzpicture}
\begin{loglogaxis}[
    width=.49\textwidth,
    xlabel={Mesh size $h$},
%    ylabel={$L^2$ errors}, 
    xmax=1.5,
    ymin=1e-4, ymax=.5,
    legend pos=south east, legend cell align=left, legend style={font=\tiny},	
    xmajorgrids=true, ymajorgrids=true, grid style=dashed,
    legend entries={Lobatto, Gauss}%, Lobatto-Gauss}    
]
\pgfplotsset{
cycle list={{blue, mark=*}, {red, dashed ,mark=square*}}%,{black, dashdotted ,mark=triangle*}}
}
% N = 1
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.225344)(0.5,0.165699)(0.25,0.0820851)(0.125,0.0494277)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.222488)(0.5,0.144629)(0.25,0.073849)(0.125,0.0217714)};

% N = 2
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.2011)(0.5,0.0658348)(0.25,0.0233793)(0.125,0.00727696)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.159118)(0.5,0.0478442)(0.25,0.0177047)(0.125,0.00421538)};

>>>>

\begin{figure}
\centering
%\subfloat[Coarse $N=3$ non-conforming affine mesh]{\raisebox{2.6em}{\includegraphics[width=.475\textwidth]{figs/mesh_affine.png}}}
\subfloat[$L^2$ errors]{
\begin{tikzpicture}
\begin{loglogaxis}[
    width=.49\textwidth,
    xlabel={Mesh size $h$},
    ylabel={Error}, 
    xmax=1.5,
    ymin=5e-6, ymax=.1,
    legend pos=south east, legend cell align=left, legend style={font=\tiny},	
    xmajorgrids=true, ymajorgrids=true, grid style=dashed,
    legend entries={Lobatto, Gauss}%, Lobatto-Gauss}    
]
\pgfplotsset{
cycle list={{blue, mark=*}, {red, dashed ,mark=square*}}%,{black, dashdotted ,mark=triangle*}}
}
% N = 1
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0300089)(0.5,0.02037)(0.25,0.0103349)(0.125,0.00395744)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0309619)(0.5,0.0201996)(0.25,0.00698411)(0.125,0.0018293)};

% N = 2
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0252826)(0.5,0.00898116)(0.25,0.00161751)(0.125,0.000284006)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.0237929)(0.5,0.00638897)(0.25,0.000964247)(0.125,0.000126189)};

@@

\node at (axis cs:2.4,2.8) {$N = 1$};
\node at (axis cs:2.4,1.3) {$N = 2$};
\node at (axis cs:2.4,.6) {$N = 3$};
\end{loglogaxis}
\end{tikzpicture}
}
\hspace{.1em}
\subfloat[$L^{\infty}$ errors]{
\begin{tikzpicture}
\begin{loglogaxis}[
    width=.49\textwidth,
    xlabel={Mesh size $h$},
%    ylabel={$L^2$ errors}, 
    xmax=1.5,
    ymin=1e-4, ymax=.5,
    legend pos=south east, legend cell align=left, legend style={font=\tiny},	
    xmajorgrids=true, ymajorgrids=true, grid style=dashed,
    legend entries={Lobatto, Gauss}%, Lobatto-Gauss}    
]
\pgfplotsset{
cycle list={{blue, mark=*}, {red, dashed ,mark=square*}}%,{black, dashdotted ,mark=triangle*}}
}
% N = 1
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.225732)(0.5,0.175585)(0.25,0.0875643)(0.125,0.050868)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.221903)(0.5,0.144126)(0.25,0.0724546)(0.125,0.0219034)};

% N = 2
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.198065)(0.5,0.0693157)(0.25,0.024472)(0.125,0.00612038)};
\addplot+[semithick, mark options={solid, fill=markercolor}]
coordinates{(1,0.178736)(0.5,0.0575655)(0.25,0.016464)(0.125,0.0029831)};
